Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions

### 2022-04-20 02_paper/02_study/paper_methods.Rmd
table fix

```{r setup, include = FALSE}
knitr::opts_chunk$set(include = FALSE)
library("papaja")
r_refs("r-references.bib")
```

@@

```{r demographicstable, echo=FALSE}

@@

# format and insert table in manuscript
demo.table %>%
papaja::apa_table(
  caption = "Demographic Information and Teaching Experience",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

@@

```{r presence_questionnaire, echo=FALSE, results='asis'}

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(include = FALSE)
library("papaja")
r_refs(file = "r-references.bib")
```

@@

```{r demographicstable, include = TRUE, echo=FALSE}

@@

# format and insert table in manuscript
demo.table %>%
papaja::apa_table(
  caption = "Demographic Information and Teaching Experience",
  # note = "Write Note here",
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "tiny" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

@@

```{r presence_questionnaire, include=TRUE, echo=FALSE, results='asis'}
